---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Workflow-for-automated-detection-and-classification-gibbon-calls

This is the code for Clink et al. 2023 (full citation below). Please cite this publication if using or reproducing any of the code or figures included here.


Clink, D. J., Comella, I.A.*, Ahmad, A.H. & H. Klinck. (2023). A workflow for the automated detection and classification of female gibbon calls from long-term acoustic recordings. Frontiers in Ecology and Evolution. 11:1071640. doi: 10.3389/fevo.2023.1071640

### Part 1. Random iterations
This code 

### Part 2. Performance metrics on validation dataset

### Part 3. Performance metrics on test dataset

### Part 4. Compare manual and automated annotations

### Part 5. Unsupervised clustering of true/false positives

### Part 6. Unsupervised clustering of female calls

### Part 7. Female call exemplar plots




```{r , echo = FALSE}

```


