---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Workflow-for-automated-detection-and-classification-gibbon-calls

This is the code for Clink et al. 2023 (full citation below). Please cite this publication if using or reproducing any of the code or figures included here.


Clink, D. J., Kier, I.A.*, Ahmad, A.H. & H. Klinck. (2023). A workflow for the automated detection and classification of female gibbon calls from long-term acoustic recordings. Frontiers in Ecology and Evolution. 11:1071640. doi: 10.3389/fevo.2023.1071640

# Quick start guide
## You can install the development version of the R package 'gibbonR' from [GitHub](https://github.com/DenaJGibbon) with:
```{r, eval=FALSE,warning=FALSE, results='hide'}
install.packages("devtools")
devtools::install_github("DenaJGibbon/gibbonR")
library(gibbonR)
```

## Tutorial for gibbonR
https://denajgibbon.github.io/gibbonR-tutorial/

## You can download the required data from Zenodo: 
Download and unzip files to a local drive that can be accessed using R. doi: 10.5281/zenodo.7562095

# R script descriptions
### Part 1. Random iterations
This script randomly subsets the training data into subsets (n= 10,20,40,80,160,320,400) over 10 iterations. The varying numbers of training data are used in the detector/classifier over the validation data set. 

### Part 2. Performance metrics on validation dataset
This script calculates area under the curve and F1 score for all of the random iterations.
```{r , echo = FALSE,dpi=300,out.width="50%",out.height="50%"}
grid::grid.raster( tiff::readTIFF( "Figures/Frontiers Figures 5.tiff")) 
```

### Part 3. Performance metrics on test dataset
This script calculates the final performance metrics on the test dataset. 

### Part 4. Compare manual and automated annotations
This script compares the automated detections output by the system with manual annotations done by a human observer using LTSAs.  
  
```{r , echo = FALSE,dpi=300,out.width="50%",out.height="50%"}
grid::grid.raster( tiff::readTIFF( "Figures/Frontiers Figures 6.tiff")) 
```


### Part 5. Unsupervised clustering of true/false positives
This script uses affinity propagation clustering on labeled true/false positives.
```{r , echo = FALSE,dpi=300,out.width="50%",out.height="50%"}
grid::grid.raster( tiff::readTIFF( "Figures/Frontiers Figures 7.tiff")) 
```


### Part 6. Unsupervised clustering of female calls
This script uses affinity propagation clustering on high-quality female gibbon calls.
```{r , echo = FALSE,dpi=300,out.width="50%",out.height="50%"}
grid::grid.raster( tiff::readTIFF( "Figures/Frontiers Figures 8.tiff")) 
```


### Part 7. Female call exemplar plots
This script plots cluster assignment by recorder location and adds an exemplar spectrogram to the plot.

```{r , echo = FALSE,dpi=300,out.width="50%",out.height="50%"}
grid::grid.raster( tiff::readTIFF( "Figures/Frontiers Figures 9.tif")) 
```


